\documentclass[a4paper,18pt]{article}
\begin{document}
\noindent
\textbf{Ankush Singh}\\
Department of Electrical Engineering\\
Indian Institute of Technology Kanpur, India\\
\textit{Email: anksingh@iitk.ac.in}
\vspace{1pc}
\hline \hline
\noindent
My academic interests are in Communication Systems and Computer architectures.
\hline \hline
\vspace{1pc}
\textbf{Education}
\begin{table}[ht]
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
{\bf Degree} & {\bf Year} & {\bf Institute/School } & {\bf CGPA/$\%$ }\\
\hline
BTech & 2020 & Indian Institute of Technology Kanpur & X.XX/10.0 \\
\hline
Class XII & 2015 & Convent of Gagan Bharti Sr. Sec. School & XX.X$\%$\\
\hline
Class X & 2013 & Convent of Gagan Bharti Sr. Sec. School & XX.X$\%$\\
\hline
\end{tabular}
\label{table:simple}
\end{center}
\end{table}\\
\textbf{Course Details}
\begin{table}[ht]
\begin{center}
\begin{tabular}{|c|c|c|}
\hline
{\bf Semester} & {\bf Total Credits} & {\bf Highlights}\\
\hline
Aug 2015-Dec 2015 & 51 & MTH101 \\
\hline
Jan 2016-Apr 2016 & 47 & MTH102,ESC101 \\
\hline
Aug 2016-Dec 2016 & 59 & ES0207,EE200 \\
\hline
Jan 2017-Apr 2017 & 63 & MSO201,ESO203,EE250 \\
\hline
Aug 2017-Dec 2017 & 65 & CS771,EE370 \\
\hline
Jan 2018-Apr 2018 & 57 & CS657,CS220,CS251 \\
\hline
\end{tabular}
\label{table:simple}
\end{center}
\end{table}\\
\textbf{Skills}
\begin{itemize}
\item Programming Languages : C, C++, Java, Python, Bash ,\LaTeX
\item Softwares/Libraries : ROS , Matlab ,OpenCV, Eclipse, SolidWorks.
\end{itemize}
\textbf{Projects}
\begin{enumerate}
\item \textbf{Obstacle Avoidance using a new selective strategy} : Aimed to improve the robot-navigation guidance strategy of Pioneer-P3DX through a vision-based selective approach
The approach was to compare the optical flow of the centre with a suitable threshold value and then selectively tune the
guidance in order to differentiate between the case of symmetry of obstacles from the case of a free field .
\item \textbf{Autonomous Chess Playing Robot}: Aim was to make an intelligent robot that can play Grandmaster -level chess using MiniMax algorithm. Designed and fabricated the arm of the robot in SolidWorks using principles of inverse kinematics in accordance with the available motor specifications and finally simulated the design (URDF format) using Ros-Moveit Assistant.
\end{enumerate}
\textbf{Awards and Achievements}
\renewcommand{\labelitemi}{\textendash}
\begin{itemize}
\item Secured All India Rank -940 in JEE 2015
\item Received KVPY Fellowship with an AIR of 808 among 1 Lakh students
\item Awarded Certificate of Merit in $15^{th}$ National Science Olympiad
\item Awarded Academic Excellence Award for outstanding academic performance in year 2015-16
\item Awarded Certificate of Merit from CBSE for having secured a CGPA of 10.0/10.0 in matriculation.
\end{itemize}
\textbf{Extra-curricular activites}
\renewcommand{\labelitemi}{\textendash}
\begin{itemize}
\item \textbf{Student Guide} and \textbf{Academic Mentor}  in Counselling Service, IIT Kanpur - guided personally a group of six freshmen in their initial period of arrival.
\item Participated in Chess competitions in Udgosh -annual sports festival of IIT Kanpur.
\item Actively participate in Bhaktivedanta Group where  study of Bhagavad Gita and other vedic scriptures take place regularly.
\end{itemize}
\end{document}